---
title: "DV_RProject3"
output: html_document
---

**Authors: Rolando Melendez, Hyunji Seo, Catherine Tu**

##This is how our RStudio is configured:
```{r}
sessionInfo()
```
***
##Program file structure
  00 Doc - contains .Rmd and .html 
  
  01 Data - contains the code to Extract, Transform, and Load our data 
  
  02 Data Wrangling - contains our workflows and the code for the visualizations 

***  
##Data summary and subset
```{r}
#Shows the subset and summary of the data frame
source("../01 Data/R_Load_Crime.R", echo = TRUE)
source("../01 Data/R_Load_Health.R", echo = TRUE)
source("../01 Data/R_Load_PublicSchools.R", echo = TRUE)
source("../01 Data/R_Load_Socioeconomic.R", echo = TRUE)
```

####Explanation of Data:
These data sets were obtained from the City of Chicago Data Portal (https://data.cityofchicago.org/). All three of our visualizations utilized the Chicago_Crimes dataset and implemented an inner join, full join, and right join, each with a different data set.

##Socioeconomic Indicators
```{r}
#Shows the subset and summary of the data frame
source("../02 Data Wrangling/SocioEconomic_Crimes.R", echo = TRUE)
```

####Findings:
This visualization aimed to examine the relationship of crime in Chicago in 2015 and Socioeconomic factors. For this visualization, we utilized a semi join between the two datasets, with Community Area number as the common measure. Although there are more than 25 different types of crime given through the data set, we limited our analysis to the top eight crime types determined by the highest count of data points.

From this visualization, we can see that the Hardship Index is similar across types of crime for a specific community area. The Hardship Index is indicative of the community environment, just like the other measures like unemployment and income level. Therefore, it seems reasonable to conclude that the crime and hardship levels are consistent within a given community, whether for better or for worse.

***

##Health Demographic Indicators
```{r}
#Shows the subset and summary of the data frame
source("../02 Data Wrangling/HealthDemographics_Crimes.R", echo = TRUE)
```

####Findings:
This visualization aimed to examine the relationship of crime in Chicago in 2015 and Health Demogrphics. For this visualization, we utilized a full join between the two datasets, with Community Area number as the common measure. This visualization focused on an 8 count spread of 31 total crime types ranging from high to low count of data points. The two visualizations focus on teen birth rate and overall birth rate, respectively. This plots each birthrate on the x-axis and homicide counts on the y-axis.

From the visualizations we can see that in general the distribution as shown in the boxplots for each crime type is very similar between the teen and the overall birth rate data. What can be seen is that for seemingly "less dangerous" crimes (Other Nacotic Violation, Sex Offense, and Theft) the range of the spread of homicide is on the low end. What is clearly apparent is that the birthrate for the overall city seems to have a slightly more steady and stagnant growth in homicide when compared to that of the teen birth rates. In teen birth rates there is a clear correlation between higher birthrate and higher homocide rates. This makes it seem that the more teens get pregnant and give birth the higher their corresponding crime rates are.

***

##Public School Safety and Student Conduct Indicators
```{r}
#Shows the subset and summary of the data frame
source("../02 Data Wrangling/PublicSchool_Crimes.R", echo = TRUE)
```

####Findings:
This visualization examines the correlation of a public school's Safety Rating and its Rate of Student Misconduct for schools in areas with records of Narcotics crime. We utilized an inner join between the two datasets of Public School Ratings and Crime, with Community Area code as the common measure. We particularly focus on how Narcotics, as one of the more frequently occurring crime types in Chicago, may play a part in the rating and student conduct in public schools located near such crimes.

Unsurprisingly, we find that as Safety Ratings decrease, Misconduct Rates shift upwards. However, there are still high outliers within the schools of "Very Strong" and "Strong" safety ratings, which suggests that there may be other types of crime that may influence the student misconduct at those schools.

***
